### 2023-10-24 manuscript.tex
Added Pfam overlap method

% TODO: Add Pfam overlap subsection

>>>>

\subsection{Calculation of Pfam domain overlaps}
The Pfam-A models (version 36.0) were downloaded from InterPro. The \textit{D. melanogaster} sequences were extracted from the alignments and searched against the Pfam models using HMMER 3.4 with a per-domain reporting threshold (option -{}-domE) of $1 \times 10^{-10}$. Overlap fractions for each region were calculated as the number residues overlapping with any Pfam domain hit divided by the total number of residues in that region.
